\documentclass[titlepage]{article}
\usepackage{fullpage}

\begin{document}

\title{17-614 Formal Methods\\[1ex] Project: Structural Modeling}
\author{
{\Large\textbf{Team 16}}\\[3ex]
yashanan\\[1ex] salonisi\\[1ex] halkhala\\[1ex] ktakayam}
\date{\today}
\maketitle

\newpage

\section*{Task1}
\begin{enumerate}
    \item Include an object model diagram for your system.
    \item Describe any decisions that your team made in resolving ambiguities in the English document. Also describe alternatives you considered and rejected.
    \item Describe any invariants that are not explicitly mentioned in the given document but were discovered during the modeling process.
    \item Describe an invariant that was violated by an operation in your model and how it was fixed.
    \item List the scope used for the analysis of invariant preservation. Why did you choose this scope, and why do you
think it is sufficient?
\end{enumerate}

\section*{Task2}
\begin{enumerate}
    \item Define an Alloy function called canView, which takes at least one parameter that represents some user in the
    social network, and returns the set of all content that can be viewed by that user. You may use any number of
    helper predicates or functions to define canView.
    \item You will use canView to check whether it is possible for a user to access a piece of content against the intent of
    the owner. In particular, we say that a privacy violation has occurred if a user is able to view a piece of content
    without adhering to the privacy level that is assigned to the content by its owner. For example, suppose that Alice
    and Bob are not friends, and Alice has a photo that is assigned privacy setting Friends; if Bob is able to view the
    photo, this would be considered a privacy violation. Define an Alloy assertion called NoPrivacyViolation
    to check that no such violation is possible.
    \item Does your model satisfy NoPrivacyViolation? If so, explain why. If not, include a counterexample that
    demonstrates a violation, and suggest a modification to the design of privacy settings in Nicebook. Describe
    any alternatives you considered and rejected, along with justifications for your decision.
\end{enumerate}

\section*{Task3}
\begin{enumerate}
    \item What are the strengths and weaknesses of Alloy and its tool, the Alloy Analyzer?
    \item Under what situations would you recommend its use (or not)? Why?
    \item With respect to this notation, what is the single most-important future development that would be needed to
    make it more generally useful to practitioners?
\end{enumerate}


\end{document}
